Ejemplificando art

### 2023-07-27 notebooks/example_script.Rmd
Adds some clarifying comments (for myself)

```{r base no ortogonal, include=FALSE}
b1_v1=c(1,4)
b1_v2=c(3,1)
b1_v1=b1_v1/len(b1_v1)
b1_v2=b1_v2/len(b1_v2)
Base_1=matrix(cbind(b1_v1,b1_v2),ncol=2)
```

>>>>

```{r base no ortogonal, include=FALSE}
b1_v1=c(1,4)
b1_v2=c(3,1)
b1_v1=b1_v1/len(b1_v1) # Normalized, but not necessary
b1_v2=b1_v2/len(b1_v2) # Normalized, but not necessary
Base_1=matrix(cbind(b1_v1,b1_v2),ncol=2)
```
